% resumo no segundo idioma
% como parametros devem ser passados o titulo e as palavras-chave
% no outro idioma, separados por vírgulas

\begin{englishabstract}{BiteUp: an application for macronutrient control}{macronutrients, nutrition, machine learning, food tracking, well-being}

With the growing interest in nutrition and well-being, there is an increasing demand for digital tools to assist in food tracking. Despite the availability of various technological solutions, many people still face difficulties in adequately monitoring their daily macronutrient intake, compromising the achievement of their nutritional goals. In this context, this project proposes the development of a mobile application that allows the user to log consumed foods and track, in real time, both the nutritional impact and the subjective effects of these food choices on their well-being.

The application performs automatic calculation of the amount of macronutrients consumed and remaining, facilitating daily meal planning and promoting adherence to healthier habits. Its main differentiator lies in the ability to analyze the user's individual response after each meal, transcending simple caloric and nutritional logging. Through a recurring feedback system, users can report aspects related to their post-prandial state, such as energy level, mood, disposition, and possible physical discomforts.

The collected data are processed to identify behavioral and nutritional patterns, enabling inferences about which foods contribute to positive or negative sensations. With the accumulation of information, the system becomes progressively more accurate in its recommendations, dynamically adapting to each user's individual needs and preferences. In addition to nutritional monitoring functionalities and food inventory, the solution incorporates machine learning techniques to offer an adaptive and personalized experience.

The project also considers essential challenges related to the accuracy of nutritional information, interface usability, and personal data security. Thus, it seeks to develop an efficient, reliable tool focused on promoting a diet that effectively contributes to the physical and emotional balance of individuals.

\end{englishabstract}